%----------------------------------------------------------------------------------------------%
%                                           Packages                                           %
%----------------------------------------------------------------------------------------------%
\usepackage{booktabs}
\usepackage[english]{babel}
\usepackage[squaren,cdot]{SIunits}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{CormorantGaramond}
\usepackage{xspace}
%-----------------------------------------------------------------------------------------------
\usepackage[hyperindex,breaklinks]{hyperref} % Required for hyperlinks
%----------------------------------------------------------------------------------------------%
%                                           Commands                                           %
%----------------------------------------------------------------------------------------------%
\hypersetup{%
    hidelinks,
    colorlinks,
    breaklinks=true,
    urlcolor=color3,
    citecolor=color1,
    linkcolor=color1,
    bookmarksopen=false,
    pdftitle={Title},
    pdfauthor={Author}
}
%-----------------------------------------------------------------------------------------------
\setlength{\abovecaptionskip}{4pt}
\setlength{\columnsep}{5.5mm}
\setlength{\columnseprule}{0.2pt}
\setlength{\fboxrule}{0.4pt} % Width of the border around the abstract
%-----------------------------------------------------------------------------------------------
\definecolor{color1}{RGB}{0,0,90} % Color of the article title and sections
\definecolor{color2}{RGB}{0,20,20} % Color of the boxes behind the abstract and headings
\definecolor{color3}{RGB}{0,0,192} % Color of the article title and sections
%-----------------------------------------------------------------------------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
%-----------------------------------------------------------------------------------------------
\newcommand{\XXX}[1]{\relax}
%----------------------------------------------------------------------------------------------%
%                                           Metadata                                           %
%----------------------------------------------------------------------------------------------%
\makeatletter
\immediate\write18{datelog > \jobname.info}
\makeatother
%-----------------------------------------------------------------------------------------------
% Journal information
\JournalInfo{engrXiv}
\Archive{Compiled on \input{\jobname.info} -- Version \input{PreprintVersion.tex}}
% Article title
\PaperTitle{Bravais Lattice Naming Schemes for Lattice-Boltzmann Methods}
\Authors{%
    C.~Naaktgeboren\textsuperscript{1$\star$},
    F.~N.~de Andrade\textsuperscript{2}
}
\affiliation{%
    \textsuperscript{1}%
    \textit{%
        Adjunct Professor.
        Universidade Tecnológica Federal do Paraná -- UTFPR, Câmpus Guarapuava.
        Grupo de Pesquisa em Ciências Térmicas.
}}
\affiliation{%
    \textsuperscript{2}%
    \textit{%
        Universidade Tecnológica Federal do Paraná -- UTFPR, Câmpus Guarapuava.
        Grupo de Pesquisa em Ciências Térmicas.
}}
\affiliation{%
    \textsuperscript{$\star$}%
    \textbf{Corresponding  author}: NaaktgeborenC$\cdot$PhD@gmail$\cdot$com
}
\Keywords{%
    Bravais lattice ---
    lattice-Boltzmann stencils ---
    lattice naming scheme ---
    method of prescribed abscissas ---
    space-filling lattices ---
    high-order lattices ---
    square lattices ---
    hexagonal lattices.
}
\newcommand{\keywordname}{Keywords}
\Highlights{%
    Proposes an unambiguous, more descriptive lattice naming scheme for LBM ---
    Lattice naming scheme is based on microscopic kinetic energy levels
}
\newcommand{\highlightname}{Highlights}
%-----------------------------------------------------------------------------------------------
\Abstract{%
    Lattice configuration is a central parameter in Lattice-Boltzmann (LB)  methods,  both  from
    theoretical and implementation standpoints. As LB methods  have  progressed  over  the  past
    decades, a variety of lattice configurations have been proposed and refered to according  to
    a plurality of lattice naming schemes that usually include the lattice \emph{velocity count}
    in their format. The so-called space-filling, or, Bravais lattice types  are  of  particular
    interest for hydrodynamic and hydro-thermal applications in the sense that the resulting  LB
    methods are capable of resolving convection in an exact fashion, thus avoiding the  artifact
    of spurious numerical diffusion. The appearance of  higher-order  LB  methods,  that  employ
    progressivelly  broader  velocity-space  discretizations  by  means  of  progressively  more
    numerous lattice velocity sets, has led to the appearance of ambiguous  velocity-count-based
    lattice nomenclatures that often require further information---usually  the  entire  set  of
    velocity vectors, or, conversely, energy levels---for an unambiguous description. This  work
    proposes a concise yet  unambiguous  naming  scheme  for  regular,  space-filling  (Bravais)
    lattices for LB methods based on \emph{lattice energy levels}  in  one  to  three  Euclidean
    spatial dimensions for lattices of \emph{any} finite size. The proposed naming scheme  leads
    to distiguisheable and unambiguously named lattices and applies a uniform rule.
}
%-----------------------------------------------------------------------------------------------
